An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-09 poly-embed-journal/poly-embed-journal.tex
Some inital changes from meeting; updating ordered partition figure

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\inter}{\mathrm{inter}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}_\red}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\begin{theorem}\label{thm:embed-poly-informal}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{theorem}

\begin{theorem}\label{thm:link-informal}
  Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{theorem}

@@

\begin{definition}
  \label{def:calibrated}
  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Given feature space $\X$, \jessie{and any?}fix a distribution $D \in \Delta(\X\times\Y)$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.

@@

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
\raf{Forward ref \S~\ref{sec:min-rep-sets} <-- add ref to 6.2}

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
\raf{Reference Theorem~\ref{thm:embed-poly-informal}}

@@

\raf{TODO: smooth over these paragraphs.  I think we should combine the first two and give only a 1-sentence description of how to achieve $|\Y|-1$ dimensions.}

Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes Risks match.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

@@

%\btw{Cut summary for now (Why is this cool?)}
%\jessiet{Jessie: added a bit to say why this is cool.}
We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.

@@

@@

The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
It is not \emph{a priori} clear that these sets even have a nonempty intersection.
We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e. if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.

@@

The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
We do so by ``thickening'' the link by $\epsilon$ as described next.
Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.
Then, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.

\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \phi(r) \in U\}$, the reports whose embedding points are in $U$.
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p} \|u^* - u\| \geq \epsilon$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.

@@

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples below, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.

@@

\raf{TODO: talk about generic approach: restrict to affine regions, take vertices}

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
For example, Hamming loss is given by $f(S) = |S|$.
In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} and here state the main results.

@@

\begin{align}\label{eq:topk-embedding}
L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} - \right)- u_y
\end{align}

@@

\begin{figure}[H]
		\centering
		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
	\label{fig:ordered-partition}
\end{figure}

@@

\subsection{Equivalent condition: matching Bayes risks}

>>>>

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\inter}{\mathrm{inter}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}_\red}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-informal}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{restatable}

\begin{restatable}{theorem}{linkinformal}\label{thm:link-informal}
  Given any polyhedral loss $L$, let $\ell$ be the discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{restatable}

@@

\begin{definition}
  \label{def:calibrated}
  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Suppose we have the feature space $\X$ and label space $\Y$.
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.
\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.
Note that in the finite-outcome setting, calibration is necessary and sufficient for consistency from a generalization of~\citet{tewari2007consistency} given by~\citet{ramaswamy2016convex}.

@@

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$ by results in \S~\ref{subsec:match-BR}.
\raf{Forward ref \S~\ref{sec:min-rep-sets} <-- add ref to 6.2}

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses, showing Theorem~\ref{thm:embed-poly-informal}.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
\raf{Reference Theorem~\ref{thm:embed-poly-informal}}

@@

\raf{TODO: smooth over these paragraphs.  I think we should combine the first two and give only a 1-sentence description of how to achieve $|\Y|-1$ dimensions.}
\jessie{Took a pass 09 Sept 21}

Note however that the number of dimensions $d$ required could be as large as $n = |\Y|$, which is particularly undesirable in structured prediction and information retrieval problems where the number of outcomes is exponential.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
Moreover, to construct an embedding of dimension $n-1$ instead of $n$, consider an invertible linear transformation from $\reals^n \to \reals^{n-1}$ and re-define the loss appropriately so Bayes risks match.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

@@

%\btw{Cut summary for now (Why is this cool?)}
%\jessiet{Jessie: added a bit to say why this is cool.}
\jessiet{Is this following paragraph necessary here?  It's more of an intro for \S~\ref{sec:calibration}.}
We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.

Recall from the introduction Theorem~\ref{thm:embed-poly-informal}.
\embedpolyinformal*
This result is exactly the chaining of theorems \ref{thm:poly-embeds-discrete} and \ref{thm:discrete-loss-poly-embeddable}, thus we have shown the result.

@@

\linkinformal* \jessie{vs...}

@@

At a high level, the proof has three main steps.
The first step is to show indirect elicitation: we give a link $\psi: \reals^d \to \R$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
%Symbolically, if $u^* \in \argmin_u \inprod{p}{L(u)} = \Gamma(p)$, then $\psi(u^*) \in \argmin_r \inprod{p}{\ell(r)} = \gamma(p)$.
For this step, the challenge is that for a generic $u \in \reals^d$, not an embedding point, we may have $u \in \Gamma(p) \cap \Gamma(p')$.
Because $u$ minimizes expected loss for both $p$ and $p'$, this \raf{suggest adding a noun here} imposes the requirement on the link that $\psi(u) \in \gamma(p) \cap \gamma(p')$.
It is not \emph{a priori} clear that these sets even have a nonempty intersection.
We use elicitation results, discussed in \S~\ref{sec:min-rep-sets}, to show that for each $u \in \reals^d$ there exists $r \in \R$ such that $\Gamma_u \subseteq \gamma_r$, i.e. if $p$ satisfies $u \in \Gamma(p)$ then it satisfies $r \in \gamma(p)$.
This implies that if $u \in \Gamma(p) \cap \Gamma(p')$, then $r \in \gamma(p) \cap \gamma(p')$, so we may safely choose $\psi(u) = r$.

@@

The second step is to ensure calibration: we should modify this link so that even approximately-optimal points $u$ link to optimal reports $r$.
We do so by ``thickening'' the link by $\epsilon$ as described next.
Informally, we take each optimal report set, i.e. some $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$, and thicken it by adding all points within distance $\epsilon$.

Finally, we impose a requirement that all points in this thickened set are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
We use $\Psi(u)$ to denote the remaining legal choices for $\psi(u)$.
After repeating for each optimal report set, we will claim that there exists a small enough $\epsilon > 0$ so that the construction is successful, i.e. $\Psi(u)$ is nonempty for all $u$.
%A key step in the following definition will be to narrow down a ``link envelope'' $\Psi$ where $\Psi(u)$ denotes the legal or valid choices for $\psi(u)$.

\begin{definition}[$\epsilon$-thickened link] \label{def:eps-thick-link}
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$ and, for each $U \in \U$, let $R_U = \{r \in \R : \phi(r) \in U\}$, the reports whose embedding points are in $U$.
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
A key point is that, by Lemma~\ref{lem:polyhedral-range-gamma}, there are only finitely many sets of the form $U = \Gamma(p)$.
We then show, along the lines discussed above, that for a small enough choice of $\epsilon > 0$, if the thickenings of $U$ and $U'$ overlap at some $u$, then the corresponding report sets $R_U, R_{U'}$ also overlap; this implies $\Psi(u)$ is nonempty.
Given a well-defined thickened link $\psi$, calibration is almost immediate because, given $p$, any report $u$ linking to a suboptimal $r = \psi(u)$ satisfies $\inf_{u^* \in \Gamma(p)} \|u^* - u\| \geq \epsilon$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.

@@

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples below, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$. \jessie{Is this true?  Not for top-$k$, unless I'm misreading}
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
%\citet{wang2020weston} apply the embedding framework to show that the Weston-Watkins hinge loss embeds a discrete loss for ordered partitions.

In general the approach to apply embeddings is as follows: given a surrogate $L:\reals^d \to \reals^\Y_+$, find the regions for which $L$ is affine.
Vertices of $L$ are formed by the intersection of $d$ facets of $\epi(L)$, or equivalently affine regions of $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
The enumeration of these vertices yields a finite representative set, and we can reason about embedding these vertices.

Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link and embedding.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Definition~\ref{def:eps-thick-link} until the last step in which values for the link are selected.
Once possible choices for this $\epsilon$-thickened set-valued function are available, we can see if the proposed link aligns with these possible choices: if so, then the proposed link is calibrated.

@@

%\raf{TODO: talk about generic approach: restrict to affine regions, take vertices} \jessie{Attempted above}

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
For example, Hamming loss is given by $f(S) = |S|$.
In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.

@@

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
		$\prop{WW}$ is shown with faint dotted lines.}
	\label{fig:ordered-partition}
\end{figure}

\begin{align}\label{eq:topk-embedding}
L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} \right)- u_y
\end{align}

@@

\subsection{Equivalent condition: matching Bayes risks}\label{subsec:match-BR}
